---
title: "Development actions history"
output: html_document
editor_options: 
  chunk_output_type: console
---

All commands that you use to use when developing packages...

# First time just after creating the project

- Fill the following chunk to create the DESCRIPTION of your package

```{r description, eval=FALSE}
# Describe your package
fusen::fill_description(
  pkg = here::here(),
  fields = list(
    Title = "Aide à la publication sur Agreste",
    Description = "Aide à la création des documents qui, après PAO, pourront être publiés sur Agreste. Facilite la cration de tableaux, graphiques, cartes. Automatise la création des chiffres et données.",
    `Authors@R` = c(
      person("Anaël", "Delorme", email = "anael.delorme@agriculture.gouv.fr", role = c("aut", "cre"), comment = c(ORCID = "0000-0002-1122-9076")),
      person("Killian", "Steunou", email = "killian.steunou@agriculture.gouv.fr", role="aut"),
      person(given = "MinAgri-SSP", role = "cph")
    )
  ),
  overwrite = TRUE
)
# Define License with use_*_license()
usethis::use_mit_license("Agreste")
```

# Start using git

```{r, eval=FALSE}
usethis::use_git()
# Deal with classical files to ignore
usethis::git_vaccinate()
```

# Set extra sources of documentation

```{r, eval=FALSE}
# README
usethis::use_readme_rmd()
# Code of Conduct
# usethis::use_code_of_conduct("contact@fake.com")
# NEWS
usethis::use_news_md()
```

**From now, you will need to "inflate" your package at least once to be able to use the following commands. Let's go to your flat template, and come back here later if/when needed.**


# Package development tools
## Use once

```{r, eval=FALSE}
# Pipe
usethis::use_pipe()

# package-level documentation
usethis::use_package_doc()

# Set CI
# _GitHub
usethis::use_github_action_check_standard()
usethis::use_github_action("pkgdown")
usethis::use_github_action("test-coverage")
# _GitLab
gitlabr::use_gitlab_ci(type = "check-coverage-pkgdown",
                       url = "https://forge.agriculture.rie.gouv.fr/gitlab/")


```

## Use everytime needed

```{r}
# Simulate package installation
pkgload::load_all()

# Generate documentation and deal with dependencies
attachment::att_amend_desc()

# Check the package
devtools::check(error_on = "error", args = "--no-exemples")
```

# Share the package

```{r}
# set and try pkgdown documentation website
usethis::use_pkgdown()

detach("package:agreste", unload = TRUE)

options(rmarkdown.html_vignette.check_title = FALSE)
options(pkgdown.internet = FALSE)

pkgdown::build_site(examples = FALSE,
                    lazy = TRUE,
                    preview = TRUE,
                    new_process = TRUE,
                    devel = TRUE)

# build the tar.gz to share with others
devtools::build()
```


# Import data
```{r}
# !!! NE PAS EXECUTER !!! (efface le fichier de data preparation)
# usethis::use_data_raw(name = "data")
```

